Low Complexity Adaptive Beamformer\\ for Active Sonar Imaging

### 2012-03-08 LCAforActiveSonarImaging/lca.tex
la2pdf commit - 2012:03:08	15:07:35	(Thu 8.Mar)
la2pdf commit - 2012:03:08	16:06:40	(Thu 8.Mar)

% \newcommand\max{\text{max}}
% \newcommand\min{\text{min}}

@@

\newcommand*\A{\mat A}
\newcommand*\B{\mat B}
\newcommand*\C{\mat C}
\newcommand*\E{\mat E}
% \renewcommand*\H{\mat H}
\renewcommand*\P{\mat P}
\newcommand*\eP{\mat{\hat P}}
\newcommand*\R{\mat R}
\newcommand*\Ri{\R^{-1}}
\newcommand*\eR{\mat{\hat R}}
\newcommand*\W{\mat W}
\newcommand*\X{\mat X}
\newcommand*\Y{\mat Y}

@@

\begin{align}
z[n] = \sumb{m=0}{M-1} w_m[n]^*x_m[n-\Delta_m] = \w\H[n]\X_\Delta[n]
\end{align}
where
\begin{align}
\w[n] = \bmat{w_0[n]\\w_1[n]\\\vdots\\w_{M-1}[n]} \qquad \text{and} \X_\Delta[n] = 
\end{align}

>>>>

% \newcommand\max{\text{max}}
\newcommand\argmin{\text{argmin}}

@@

\newcommand*\A{\mat A}
\newcommand*\B{\mat B}
\newcommand*\C{\mat C}
\newcommand*\E{\mat E}
% \renewcommand*\H{\mat H}
\renewcommand*\P{\mat P}
\newcommand*\eP{\mat{\hat P}}
\newcommand*\R{\mat R}
\newcommand*\Ri{\R^{-1}}
\newcommand*\eR{\mat{\hat R}}
\newcommand*\W{\mat W}
\newcommand*\X{\mat X}
\newcommand*\Xd{\X_{\!\Delta}}
\newcommand*\Y{\mat Y}

@@

\begin{align}
z[n] = \sumb{m=0}{M-1} w_m[n]^*x_m[n-\Delta_m] = \w\H[n]\Xd[n]
\end{align}
where
\begin{align}
\w[n] = \bmat{w_0[n]\\w_1[n]\\\vdots\\w_{M-1}[n]} \quad \text{and} \quad\Xd[n] = \bmat{x_0[n]\\x_1[n]\\\vdots\\x_{M-1}[n]}.
\end{align}

Minimum variance distortionless resonse
\begin{align}
\underset{\w[n]}{\argmin}\, E\{ |z[n]|^2 \} = \underset{\w[n]}{\argmin}\, \w\H[n]\R[n]\w[n], 
\end{align}
subject to
\begin{align}
\w\H[n]\a = 1,
\end{align}
where
\begin{align}
\R[n] = E\{ \x\x\H \}.
\end{align}s<
If $\eR$ is the estimate of $\R$, the solution to the MVDR beamformer is
\begin{gather*}
\vec w[n] = \frac{\hat{\mat R}\,\!^{-1}[n]\vec a}{\vec a\H\hat{\mat R}\,\!^{-1}[n]\vec a} = \frac{\text{\raisebox{1.9pt}{$\vec\chi$}}[n]}{\vec a\H\text{\raisebox{1.9pt}{$\vec\chi$}}[n]}
\end{gather*}
A robust estimate of $\eR$ is found by
\begin{itemize}
\item Spatial averaging to decorrelate noise from signal. \emph{Subarray averaging} used here.
\item Temporal averaging to ensure valid speckle statistics.
\item \emph{Diagonal loading} to ensure  numerical stability prior to inversion.
\item Choice of robustification parameters (C-I) \cite{}
\end{itemize}

\section{Results}
